### 2015-05-01 latex/phd_thesis.tex
Tidying main matter

\usepackage[pdftex,
            pdfauthor={Your Name},
            pdftitle={Thesis},
            pdfsubject={Dissertation},
            pdfkeywords={microarray gene expression statistical models regression},
            pdfproducer={Latex with hyperref, or other system},
            pdfcreator={pdflatex, or other tool}]{hyperref}

@@

\begin{itemize}
  \item Some data in my thesis are mapped to hg18 and some to hg19.
  \item Include summary of notation?
\end{itemize}

The data sets used in this thesis were provided by the investigators listed below.\\\\

@@

Equally, my PhD would not be possible without the countless people who contribute to the software I use in my daily research. A special thanks to those who helped me as I learnt to write software of my own: Felix Krueger, Toby Sargeant, Martin Morgan, Hervé Pagès, Hadley Wickham and Dirk Eddelbuettel. Open software is the best software.

@@

I owe an enourmous debt of gratitude to my thesis writing buddies, Hannah Vanyai and Darcy Moore, who kept me going during tough times and to my thesis proof readers, Belinda Phipson, Saskia Freytag and Goknur Giner, who have greatly improved this thesis.

\textbf{TODO: final thanks}

Finally, and most of all, thank you to my parents, Gay and John, to my brothers, Jack, Luke and Daniel, and to my friends. Words cannot express

@@

% TODO: Check list of abbreviations
\chapter{List of Abbreviations}

\begin{tabular}{ll}

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMC & differentially methylated cytosine \\
DMR & differentially methylated region \\
HMM & hidden Markov model \\
SE & single-end sequencing \\
PE & paired-end sequencing \\
indel & insertion or deletion \\
CGI & CpG island \\

\end{tabular}

% TODO: Check list of symbols
\chapter{List of Symbols}

\begin{tabular}{ll}

i.e. & that is\\

\end{tabular}

>>>>

\usepackage[pdftex,
            pdfauthor={Your Name},
            pdftitle={Thesis},
            pdfsubject={Dissertation},
            pdfkeywords={DNA methylation bioinformatics applied statistics epigenetics epigenomics},
            pdfproducer={Latex with hyperref, or other system},
            pdfcreator={pdflatex, or other tool}]{hyperref}

@@

The data sets used in this thesis were provided by the investigators listed in Chapter \ref{chap:datasets}.\\\\

@@

Equally, my PhD would not be possible without the countless people who contribute to the software I use in my daily research. A special thanks to those who helped me as I learnt to write software of my own: Felix Krueger, Toby Sargeant, Martin Morgan and Hervé Pagès. Open software is the best software.

@@

I owe an enormous debt of gratitude to my thesis writing buddies, Hannah Vanyai and Darcy Moore, who kept me going during tough times and to my thesis proof readers, Belinda Phipson, Saskia Freytag and Goknur Giner, who have greatly improved this thesis.

Finally, and most of all, thank you to my parents, Gay and John, to my brothers, Jack, Luke and Daniel, and to my friends. Your support, love and encouragement kept me going.

@@
